Initial Analysis

### 2020-08-06 Scripts/Initial_Analysis.Rmd
Updated supplement table S2
Changes to graphs

  if(Variable_Selected == "catch"){
    Map_Label <- "Catch (Thousand Tons)"
    Plot_Name <- "Catch_plot.png"
  }else{
    Map_Label <- "Revenue (Million USD)"
    Plot_Name <- "Rev_plot.png"
  }

@@

  Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
  Labels <- c("(1-10]",paste(Bins[2:5]))

@@

    plot_all <- ggdraw() +
      # map
      draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
      # Revenue circular
      draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
      # Catch circular
      draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
      # Labeks
      draw_plot_label(label = c("a", "b"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(1, 0.45)
      ) +
      draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
                      size = 8,
                      x = c(0.330,0.485), 
                      y = c(0.31,0.29)
      )

@@

Discrete_Exclusive %>% 
  semi_join(Tresholded_T_Data, by = "taxon_key") # 0 ok thes

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1,000,5000,12000)

@@

@@

#### Supplemental Table 3

# T_Summary %>%
#   left_join(D_Summary, by = "observation") %>%
#   mutate(
#     "Mean Shared" = paste(round(`mean(value).x`,2)," \u00B1 (",round(`sd(value).x`,2),")",sep=""),
#     "Mean Discrete" = paste(round(`mean(value).y`,2)," \u00B1 (",round(`sd(value).y`,2),")",sep="")
#     ) %>%
#   select(1,8:9) %>%
#   filter(observation != "No Category") %>%
#   rename(Category = observation) %>%
#   arrange(Category) %>%
#   write_csv("Category_summary.csv")

@@

# Discrete Data
Discrete_Data_Stats <- Discrete_Status_Data %>% 
  filter(observation != "No Category") %>%
  mutate(value = abs(value))

@@

Manova_Differences <- Transboundary_Data_Stats %>% 
  rename(Trans_value = value) %>% 
  left_join(Discrete_Data_Stats, by = c("individual","observation","group")
  ) %>% 
  rename(Discrete_value= value) %>% 
  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value))

@@

mano <- manova(cbind(Discrete_value,Trans_value) ~ observation, data = Manova_Differences)

@@

@@

@@

TukeyHSD(Stat_discrete_cat_aov)
# 
#  diff         lwr       upr     p adj
# Category B-Category A 3.627759 -0.02854633  7.284065 0.0523425
# Category C-Category A 9.917391  6.31117452 13.523608 0.0000000
# Category C-Category B 6.289632  2.79874173  9.780522 0.0000835

@@

@@

Ecosystem_plots <- Country_Spp_Data %>%
  ungroup() %>% 
  mutate(name = reorder_within(fishing_entity,top_catch,group)) %>% # to order the facet wrap
  ggplot() +
  geom_bar(
    aes(
      x = name,
      y = top_catch/1000,
      fill = group
    ), 
    stat = "identity"
  ) +
  labs(x = "",
       y = "Catch (Thousand tonnes)") +
  scale_fill_manual("",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 3, name = "Darjeeling2")
                    ),
                    na.value = "white"
  ) +
  facet_wrap(~group,
             nrow=2,
             scales = "free") +
  # ggtheme_plot() +
  my_ggtheme_p() +
  scale_x_reordered() +
  theme(legend.position = "",
        axis.text.x = element_text(size = 11,
                                   angle = 0,
                                   face = "plain"),
        strip.background = element_blank(),
        strip.text.x = element_blank()
  )

>>>>

  if(Variable_Selected == "catch"){
    Map_Label <- "Catch (Thousand Tonnes)"
    Plot_Name <- "Catch_plot.png"
  }else{
    Map_Label <- "Revenue (Million USD)"
    Plot_Name <- "Rev_plot.png"
  }

@@

  # Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
  Labels_Trans <- c("(1-29]","(29-57]","(57-85]","(85-113]","(113-141]")
  # Labels <- c("(1-10]",paste(Bins[2:5]))
  Labels <- c("(1-10]","(10-100]","(100-1000]","(1000-5000]","(5000-12000]")

@@

    plot_all <- ggdraw() +
      # map
      draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
      # Revenue circular
      draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
      # Catch circular
      draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
      # Labeks
      draw_plot_label(label = c("a", "b"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(1, 0.45)
      ) +
      draw_plot_label(label = c("Revenue (USD) | Catch (Tonnes)","(Million)"), 
                      size = 8,
                      x = c(0.325,0.485), 
                      y = c(0.31,0.29)
      )

@@

# Discrete_Exclusive %>% 
#   semi_join(Tresholded_T_Data, by = "taxon_key") # 0 ok thes

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1000,5000,12000)

@@

#--------------------------- #
### Create Suplemental Table S1
#--------------------------- #

Subregion_Trans_raw_Value %>% 
  select(sub_region,Size_Entity_sum) %>% 
  distinct(sub_region,.keep_all = TRUE) %>% 
  write_csv(.,
            "Table_S1.csv")

#--------------------------- #

@@

#### Supplemental Table S2

T_Summary %>%
  left_join(D_Summary, by = "observation") %>%
    write_csv("Table_S2.csv")

# -------------------------- #
# Soley Discrete data
# -------------------------- #

Exclusive_Discrete_Status_Data <- Discrete_Exclusive %>% 
  left_join(Status_Data, 
            by =c("eez_name","taxon_key")
  ) %>%
  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
  group_by(fishing_entity,status) %>% 
  summarise(value = length(unique(taxon_key))) %>% 
  left_join(UN_Regions, by ="fishing_entity") %>%
  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  # mutate(value = ifelse(value > 100,100,value)) %>% 
  filter(!is.na(fishing_entity),
         !str_detect(fishing_entity, ".\\(.") # remove associated territories
  ) %>% 
  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
  arrange(group,value) %>% 
  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
                              ifelse(observation == "Max Exploited","Category B",
                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                              )
         )
  ) %>% 
  group_by(individual,observation,group) %>% 
  summarise(value = sum(value))

@@

# Discrete Data (trans.not shared)
Trans_Dis_Data_Stats <- Discrete_Status_Data %>% 
  filter(observation != "No Category") %>%
  mutate(value = abs(value))

# Discrete Data (just desrete and not trans.not shared)
Discrete_Data_Stats <- Exclusive_Discrete_Status_Data %>% 
  filter(observation != "No Category") %>%
  mutate(value = abs(value))

@@

Manova_Differences <- Transboundary_Data_Stats %>% 
  rename(Trans_value = value) %>% 
  left_join(Discrete_Data_Stats, by = c("individual","observation","group")
  ) %>% 
  rename(Discrete_value= value) %>% 
  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value)) %>% 
  left_join(Trans_Dis_Data_Stats, by = c("individual","observation","group")) %>% 
  rename(Trans_Discrete_value= value) %>% 
  mutate(Trans_Discrete_value = ifelse(is.na(Trans_Discrete_value),0,Trans_Discrete_value))

@@

mano <- manova(cbind(Discrete_value,Trans_value,Trans_Discrete_value) ~ observation, data = Manova_Differences)

@@

# 
#             Df  Pillai approx F num Df den Df    Pr(>F)    
# observation   2 0.17329   21.771      4    918 < 2.2e-16 ***
# Residuals   459                                             
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

summary.aov(mano)

@@

# New only comparing shared trans to discrete exclusive
# Kruskal-Wallis chi-squared = 50.723, df = 13, p-value = 2.24e-06

@@

@@

Trans_Dis_Data_Stats

@@

Ecosystem_plots <- Country_Spp_Data %>%
  ungroup() %>% 
  mutate(name = reorder_within(fishing_entity,top_catch,group)) %>% # to order the facet wrap
  ggplot() +
  geom_bar(
    aes(
      x = name,
      y = top_catch/1000, # thusand tons
      fill = group
    ), 
    stat = "identity"
  ) +
  labs(x = "",
       y = "Catch (Thousand tonnes)") +
  scale_fill_manual("",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 3, name = "Darjeeling2")
                    ),
                    na.value = "white"
  ) +
  facet_wrap(~group,
             nrow=2,
             scales = "free") +
  # ggtheme_plot() +
  my_ggtheme_p() +
  scale_x_reordered() +
  theme(legend.position = "",
        axis.text.x = element_text(size = 11,
                                   angle = 0,
                                   face = "plain"),
        strip.background = element_blank(),
        strip.text.x = element_blank()
  )
